\chapter{Introduction}
\label{chp:introduction}
\justify{
The Agile Manifesto \cite{beck2001manifesto} drafted by Kent Beck et al. in 2001 created the Agile software development method. Since then, this new software development method has drawn attention to the industry. The Agile has become a leading standard for the software development industry, with multiple further enhancements aiming to tackle certain business-specific challenges.
}
The Agile method advocates the shorter development iteration, continuous development of software and continuous delivery of the software to the customer. The goal \cite{beck2001manifesto} of Agile is to satisfies customer with early and continuous delivery of the software.
The Agile, which aims at the improvement of the process within the software development team and the communication between the development team and costumers \cite{miglierina2014application} do makes the software development faster. However, it doesn't emphasis the cooperation and communication between the development team and other teams. In real life, the conflict and lack of communication between the development team and operation teams usually become the barrier for shortening the delivery time of the software project.
\par
Hence, in answer to how to solve the gaps and flaws when applying Agile into real-life software development, the concept of DevOps emerged. The term "DevOps" is created by Patrick Debois in 2009 \cite{kim2016devops}, after he saw the presentation "10 deployments per day" by John Allspaw and Paul Hammond. While Agile fills the gap between software development and business requirement from the customer, the DevOps eliminates the gap between the development team and the operation team \cite{WhatisaD20:online}. By eliminates the barrier we mentioned in the last paragraph, DevOps further fasten software delivery. In conclusion, DevOps means a combination of practices and culture which aims to combine separate departments(software development, quality assurance and the operation and others) in the same team, in order fasten the software delivery, maximizing delivered without risking high software quality \cite{DevOpsWi87:online}\cite{ebert2016devops}.
\par
In software engineering, the toolchain is a set of tools which combined for performing a specific objective. DevOps toolchain is the integration between tools that specialised in different aspect of the DevOps ecosystem, which support and coordinate the DevOps practices. The DevOps toolchain could assistant business in creating and maintain an efficient software delivery pipeline, simplify the task and further achieve DevOps \cite{DevOpsto7:online}. On the other hand, DevOps strongly rely on tools. There are specialised tools exist for helping teams adopt different DevOps practices \cite{zhu2016devops}. 
\par
Traditionally, the DevOps toolchain is to have individual tools which are stand-alone and from different companies. The tools usually are on-premise. But can be also deployed on cloud virtual machines. We call it
\textbf{non-integrated toolchain} in this report.
\par
At the same period that the tools for DevOps emerged and developed, the cloud technologies also developed rapidly. This leads to the emigrations of Serverless Computing. 
The Serverless Computing is a new cloud computing model which all used to build and run the application on the cloud, without thinking about the servers \cite{Serverle81:online}. It also allows developers to build the application with less overhead \cite{Serverle81:online} and more flexibility by eliminates infrastructure management tasks \cite{Serverle73:online}.
With serverless computing technologies, many new cloud technologies emerged, which gives developers an alternative way than traditional cloud servers or cloud virtual machines. For examples: Functional computing allows the application to be divided by functions and designed under event-driving paradigm without managing the hardware infrastructures. The on-demand nature of the serverless computing cloud could be used to deploy certain component of a DevOps toolchain to ease the implementation difficulties and reduce the cost. Managed scalable container services in the cloud enable the user to run the container-based application directly on the cloud, which helps the toolchain become more scalable. DevOps tools as a service \cite{DevOpsas45:online} allow the cloud provider to deliver a DevOps tool directly on its cloud platform.
\par
Helping the customer do the DevOps transformation is one of the main business activities of Eficode, the company which I'm writing my thesis. This is done by the developing and deployment of DevOps toolchain for costumers. As mentioned in the last paragraph, the new changes brought by cloud may further improve the performance and lower the cost of DevOps toolchain development -- both in money and time. As part of thesis work at Eficode, We will investigate how could serverless computing help improve the DevOps toolchain. 
\section{Problem Statement}
% Don't refer RQs here
As per the last paragraph, serverless computing gives developers alternative ways to deploy the non-integrated DevOps beside cloud virtual machines. Several cloud providers utilise serverless computing. Among them, Amazon Web Services(AWS)\footnote{https://aws.amazon.com/} has the largest market share is the first cloud provider which provides the serverless computing services. According to the report from Gartner \cite{GartnerS47:online}, the market share of AWS was 47.8\% in the year 2018 which makes it the largest cloud provider in the world.
\par
Nowadays, the serverless computing services in AWS has already been expanded to a set of fully managed services called "AWS serverless platform" \footnote{https://aws.amazon.com/serverless/}. This platform includes new AWS cloud products that leverage the serverless computing technologies. These products includes for instance, AMS Lambda\footnote{https://aws.amazon.com/lambda/} for function computing, AWS Fargate\footnote{https://aws.amazon.com/fargate/} for managed container services.
AWS also gains the most popular among the developers that using serverless technologies. The most recent survey report \cite{cncf2020} from Cloud Native Computing Foundation (CNCF) shows that 51\% of serverless users are using AWS Lambda, while 68\% of developers who are not using Kubernetes are using AWS ECS to hosting their containers.
As the Advanced AWS partner, AWS is being used as the main cloud providers in the customer projects by Eficode. And the company keeps looking for ways to leverage serverless computing services in AWS to benefit the DevOps toolchains it builds for costumers.
\par
However, despite the wide application of serverless technologies, and an enormous number of research papers about the use-case or benefit of serverless in data analysis \cite{8457831}, for container-based microservices \cite{perez2018serverless}, or for IoT applications \cite{nastic2017serverless} \cite{glikson2017deviceless}, the benefit of serverless to DevOps is not yet be discussed. There do have paper \cite{ivanov2018implementation} or book \cite{bangera2018devops} about DevOps toolchain for serverless applications. Nerveless, there still lack researches about how could serverless helps DevOps toolchain itself. Thus, our first research question is to fill the gap by answering this question. 
\par
The second area we'd like to investigate in our project is the integrated DevOps toolchain that is powered by serverless DevOps tooling in AWS. 
\par
The \textbf{integrated DevOps toolchain} is delivered as a cloud-based single platform that allows development teams to start using DevOps toolchain without the pain of having to choose, integrate, learn, and maintain a multitude of tools. In other words, the cloud based-integrated DevOps toolchain is to offering DevOps toolchain as a service
In AWS, this is offered by AWS CodePipeline (as the platform) and Several serverless tools that integrated with CodePipeline.
\par
This integrated toolchain is one of the new changes that serverless computing brings, but it also leaves a question to the development team who trying to build DevOps toolchain on AWS: which kind of toolchain should they select? Should they stick on the previous non-integrated toolchain or embracing the integrated one? The integrated DevOps toolchain provides an out-of-box integrated solution for the whole DevOps lifecycle, which is tempting, but apart from the advertisement from the vendors of these "DevOps" platforms, we still lack third party researches about the comparisons between these two. 
% So another part of our research is a case study which compares these two kinds of toolchains on different metrics. This could give the software development team a better knowledge on which kind of toolchain suites them the best.
\par
Based on the above, the research questions could be summarised as below:
\begin{enumerate}
    \item \textbf{RQ1:} How can serverless computing services in Amazon Web Services help the DevOps toolchain?
    \item \textbf{RQ2:} How does the newly emerged integrated toolchain in Amazon Web Services compared with the traditional non-integrated toolchain?
\end{enumerate}
\section{Research Approach} 
\par
To answer the RQ 1, we first investigate the current serverless offering in Amazon Web Services (AWS) which is one of the cloud services mainly used in the Eficode. We first analyze the functionality that each service has and how does these services could be used by our DevOps toolchain that deployed to AWS in Chapter 3.
\par
For answer RQ1 and RQ2, we implement both traditional non-integrated and integrated toolchain based on the DevOps practices and tools used by Eficode. In the design and implementation of the toolchain, we focus on the following DevOps practices: Version Control, Configuration Management, Continuous Delivery and Monitoring. The goal of the implementation is: First, validate the availability of using AWS serverless computing services in the traditional non-integrated toolchain. Thus in the process of developing and deploy the toolchain, we could already partly answer the RQ1 by answering how the Serverless computing services be used in our DevOps toolchain. Second, the implementation is served as the environment for experiments in Chapter 5 which could answer two RQs.
\par
To further facilitate the answer to RQ1, our next step of the study is an experiment.
The experiments are done by comparing the metrics measured from the toolchain with and without using certain serverless computing service from AWS. The metrics cover different perspectives includes cost, performance and development difficulties. 
\par
To answer RQ2, The non-integrated toolchain is used to compare with the DevOps toolchain build by the DevOps tools provided by AWS as a service.
Besides, we conduct a study on a comparison between an AWS based traditional toolchain and the out-of-box integrated DevOps toolchains also provided by AWS as services. The reason that we keep the comparison scope within AWS is that both 2 toolchains are runs on the same hardware setup provided by AWS, this could eliminate the errors caused by the difference between vendors and focuses on the difference between toolchains.
\par
In the experiment for answering RQ2, we simulate the same DevOps lifecycle of a demo Spring Boot web app on both toolchains. We again measure the metrics in these 2 toolchains, the process is similar to what we do on RQ1.
For software development teams, it could provide better insights on how to select the DevOps toolchains.
% The perspective of comparison between these toolchains will include:
% \begin{itemize}
%     \item Development time: The time spend for implements the toolchain and set up the whole DevOps pipeline.
%     \item Cost structure: The total cost for using the toolchain. For self-built toolchain, it will also include the cost decomposition (for different tools).
%     \item Flexibility: How much freedom can you add/change tools in the toolchain.
%     \item Scalability: How easy to scale the toolchain for the larger project.
%     \item Performance: The performance of the Continues Delivery pipeline, for the same task, how long will it take for the whole process?
% \end{itemize}
\section{Thesis Structure and Main Contributions}
In Chapter 2, we introduce concepts within the scope of DevOps. We also include the concepts in cloud computing which is related to our research. Chapter 3 is focusing on a survey on serverless computing technologies which the DevOps toolchain could make use of. Chapter 4 focuses on the designed and the implementation of our DevOps toolchains(both non-integrated and integrated). Chapter 5 focuses on the experiments and evaluations, which show how does the serverless computing services introduced in CH3 could benefit DevOps toolchain, and how these 2 kinds of toolchains we mentioned earlier compared with each other. We finally summarise our research and answer the research questions in Chapter 6.
\par
The main contributions of this thesis project are:
\begin{itemize}
    \item We provide a study on how could the DevOps tools leverage the cloud services to reduced development/deployment difficulties, lower the cost and improving the performance. This part of research could help the software team which is going to employ DevOps understand the practices needed. Besides, the research gives them a clearer scope of the tools needed for implementing the practices.
    \item We give the overview of 2 different types of DevOps toolchain. We also implement demo prototypes for each type of toolchain and conduct experiments with these prototypes. The experiment result shows a comparison between different toolchains. It could help the software team understand which toolchain cloud be selected based on the needs.
\end{itemize}